---
title: "p00097 re-analysis and data extraction notes"
output: 
   html_document:
      theme: cosmo
      highlight: tango
---

Despite a lack of research linking school shootings to video games, video games are frequently associated
with school shootings carried out by White perpetrators. Because there is a stereotypical association
between racial minorities and violent crime, it is possible that people often look toward video games as
a cause for school shootings committed by White perpetrators who do not fit this stereotype. Consistent
with this notion, Study 1 (n   169) found that participants who read a mock news story about a school
shooting were more likely to blame video games when the shooter was White than when the shooter was
Black. Study 2 examined 204,796 news stories of 204 mass shootings committed in the United States and
found that, when a shooting occurred at a school, video games were 8.35 times more likely to be
discussed when the shooter was White than when the shooter was Black.

```{r setup, include=TRUE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magrittr)
source("../scripts/helpers.R")

# for alternative analyses 
library(robustbase)
library(moments)

list.files("../data/raw_data/", pattern = "p00097")

p00097_tib <- readr::read_csv("../data/raw_data/p00097_makrey2019_Datastudy1.csv")

```

Study 1

compute weekly video game use 

```{r}
p00097_tib %<>% dplyr::mutate(
  hours_pw = `Hours a day playing video games`*7
)

```

They fit anova with and without covariates, I'm only reproducing the one with as it's a more complex model

```{r}
lm(`BlameGamesDV(MeanOf11dAnd11h)` ~ `IV condition (Black or White Mug)` 
   + `11b. Social environment Wilson lived in a factor in this crime`
   + hours_pw, 
   data = p00097_tib) %>% car::Anova(type = 3)
```

Model to refit: 

```{r}
p00097_mod <- lm(`BlameGamesDV(MeanOf11dAnd11h)` ~ `IV condition (Black or White Mug)` 
   + `11b. Social environment Wilson lived in a factor in this crime`
   + hours_pw, 
   data = p00097_tib)

p00097_mod %>% summary()
```


```{r}
p00097_tib <- p00097_tib %>% 
   dplyr::mutate(
      z_blame = z(`BlameGamesDV(MeanOf11dAnd11h)`),
      z_social_env = z(`11b. Social environment Wilson lived in a factor in this crime`), 
      z_hours_pw = z(hours_pw)
   )

```

```{r}
p00097_mod_z_1 <- lm(z_blame ~ `IV condition (Black or White Mug)` 
   + z_social_env
   + z_hours_pw, 
   data = p00097_tib)

summary(p00097_mod_z_1)
```

```{r}
key_effects = c("`IV condition (Black or White Mug)`White Mugshot")
export_ols(p00097_mod_z_1, key_effects)
```



