---
title: ""
output: html_document
---

Political action (volunteering, protesting) is central to functioning democracies, and action is often
motivated by negative emotion. However, theories of emotion regulation suggest that people often strive
to decrease such negative emotions. Thus, effective emotion regulation (e.g., reappraisal)—while helping
people feel better— could have the unintended consequence of hindering political action. We tested this
hypothesis in Clinton voters after the 2016 U.S. election (Ntotal   1552). Studies 1a (conducted
November 2016) and 1b (conducted November 2016, with a follow-up in January 2017) assessed
individuals’ recent use of reappraisal in managing emotions evoked by the election. Studies 2a and 2b
(conducted March 2017) exposed individuals to Trump-focused news footage and assessed individuals’
reappraisal during the clip and subsequent emotional responses. Studies 3a and 3b (conducted June 2017)
experimentally manipulated reappraisal and measured subsequent emotional responses to Trump-focused
news footage. Each study assessed recent or intended political action. In Studies 1a and 1b, we found that
reappraisal predicted lower political action; in Studies 2a and 2b we observed an indirect effect such that
reappraisal predicted lower negative emotion which in turn accounted for lower intentions to engage in
political action; and Studies 3a and 3b provided experimental evidence for this indirect effect. These
results suggest that effective emotion regulation like reappraisal may be beneficial in the short-run by
helping restore emotional well-being after upsetting political events but may also be costly in the
long-run by reducing the potential for productive political action.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magrittr)

list.files("../data/raw_data/", pattern = "p00856")

p00856_tib_1a <- haven::read_sav("../data/raw_data/p00856_ford2018_Study 1a - Data.sav")
p00856_tib_1b <- haven::read_sav("../data/raw_data/p00856_ford2018_Study 1b - Data.sav")
p00856_tib_2a <- haven::read_sav("../data/raw_data/p00856_ford2018_Study 2a - Data.sav")
p00856_tib_2b <- haven::read_sav("../data/raw_data/p00856_ford2018_Study 2b - Data.sav")
p00856_tib_3a <- haven::read_sav("../data/raw_data/p00856_ford2018_Study 3a - Data.sav")
p00856_tib_3b <- haven::read_sav("../data/raw_data/p00856_ford2018_Study 3b - Data.sav")

```

# Study 1a 

```{r}
p00856_tib_1a %<>% 
   dplyr::mutate(
      dplyr::across(
         .cols = c("Age", "USLadder"), 
         .fns = z, 
         .names = "z_{.col}"
      )
   )
```


```{r}
lm(ZAllAct_demo ~ ZElection.Reap.mean_demo + 
     Age + as.factor(Gender) + as.factor(Ethnicity_R) + USLadder, 
   data = p00856_tib_1a) %>% summary()
```

```{r}
p00856_mod_z_1 <- lm(ZAllAct_demo ~ ZElection.Reap.mean_demo + 
     z_Age + as.factor(Gender) + as.factor(Ethnicity_R) + z_USLadder, 
   data = p00856_tib_1a)
```

```{r}
key_effects = c("ZElection.Reap.mean_demo")
export_ols(p00856_mod_z_1, key_effects)
```


# Study 1b

```{r}
lm(ZT1.AllAct.Future.Sum_demo ~ ZT1.Election.ERQ.Reap.Mean_demo + 
     z(T1.Age) + as.factor(T1.Gender) + as.factor(T1.Ethnicity_R) + z(T1.LadderUS), 
   data = p00856_tib_1b) %>% summary()

```

```{r}
p00856_mod_z_2 <- lm(ZT1.AllAct.Future.Sum_demo ~ ZT1.Election.ERQ.Reap.Mean_demo + 
                        z(T1.Age) 
                     + as.factor(T1.Gender) + as.factor(T1.Ethnicity_R) + z(T1.LadderUS), 
                     data = p00856_tib_1b)
```

```{r}
key_effects = c("ZT1.Election.ERQ.Reap.Mean_demo")
export_ols(p00856_mod_z_2, key_effects)
```






```{r}
lm(ZT2.AllAct.Now.Sum_T2Z_demo ~ ZT1.Election.ERQ.Reap.Mean_T2Z_demo + 
     z(T1.Age) + as.factor(T1.Gender) + as.factor(T1.Ethnicity_R) + z(T1.LadderUS), 
   data = p00856_tib_1b) %>% summary()
```

```{r}
p00856_mod_z_3 <- lm(ZT2.AllAct.Now.Sum_T2Z_demo ~ ZT1.Election.ERQ.Reap.Mean_demo +
                        z(T1.Age)
                     + as.factor(T1.Gender) + as.factor(T1.Ethnicity_R) + z(T1.LadderUS),
                     data = p00856_tib_1b)
```

```{r}
key_effects = c("ZT1.Election.ERQ.Reap.Mean_demo")
export_ols(p00856_mod_z_3, key_effects)
```


# Study 2a 

```{r}
p00856_mod_z_4 <- lm(ZNegNoA ~ ZReapSuc
                     + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income)
                     , data = p00856_tib_2a)
```

```{r}
key_effects = c("ZReapSuc")
export_ols(p00856_mod_z_4, key_effects)
```






```{r}
p00856_mod_z_5 <- lm(ZAngry ~ ZReapSuc+ z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income)
                     , data = p00856_tib_2a)
p00856_mod_z_5
```

```{r}
key_effects = c("ZReapSuc")
export_ols(p00856_mod_z_5, key_effects)
```





```{r}
p00856_mod_z_6 <- lm(ZAllAct ~ ZNegNoA
                     + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income)
                     , data = p00856_tib_2a)
```

```{r}
key_effects = c("ZNegNoA")
export_ols(p00856_mod_z_6, key_effects)
```





```{r}
p00856_mod_z_7 <- lm(ZAllAct ~ ZAngry
                     + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income)
                     , data = p00856_tib_2a)
```

```{r}
key_effects = c("ZAngry")
export_ols(p00856_mod_z_7, key_effects)
```





```{r}
p00856_mod_z_8 <- lm(ZAllAct ~ ZReapSuc
                     + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income)
                     , data = p00856_tib_2a)


p00856_mod_z_8 %>% summary()
confint(p00856_mod_z_8)
```

```{r}
key_effects = c("ZReapSuc")
export_ols(p00856_mod_z_8, key_effects)
```


# Study 2b

```{r}
lm(ZNegNoA ~ ZReapSuc, data = p00856_tib_2b) %>% summary()
```

```{r}
lm(ZAngry ~ ZReapSuc, data = p00856_tib_2b) %>% summary()
```

```{r}
lm(ZAllAct ~ ZNegNoA, data = p00856_tib_2b) %>% summary()
```

```{r}
lm(ZAllAct ~ ZAngry, data = p00856_tib_2b) %>% summary()
```

```{r}
lm(ZAllAct ~ ZReapSuc, data = p00856_tib_2b) %>% summary()
```


-----

```{r}
p00856_mod_z_9 <- lm(ZNegNoA ~ ZReapSuc
                     + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income),
                      data = p00856_tib_2b)
```

```{r}
key_effects = c("ZReapSuc")
export_ols(p00856_mod_z_9, key_effects)
```




```{r}
p00856_mod_z_10 <- lm(ZAngry ~ ZReapSuc
                      + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income),
                      data = p00856_tib_2b)
```

```{r}
key_effects = c("ZReapSuc")
export_ols(p00856_mod_z_10, key_effects)
```




```{r}
p00856_mod_z_11 <- lm(ZAllAct ~ ZNegNoA
                      + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income),
                      data = p00856_tib_2b)
```

```{r}
key_effects = c("ZNegNoA")
export_ols(p00856_mod_z_11, key_effects)
```




```{r}
p00856_mod_z_12 <- lm(ZAllAct ~ ZAngry
                      + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income),
                      data = p00856_tib_2b)
```

```{r}
key_effects = c("ZAngry")
export_ols(p00856_mod_z_12, key_effects)
```



```{r}
p00856_mod_z_13 <- lm(ZAllAct ~ ZReapSuc
                      + z(Age) + as.factor(Gender) + as.factor(Race_R) + z(Income),
                      data = p00856_tib_2b)

summary(p00856_mod_z_13)
confint(p00856_mod_z_13)
```

```{r}
key_effects = c("ZReapSuc")
export_ols(p00856_mod_z_13, key_effects)
```






# Study 3a 

```{r}
p00856_tib_3a %<>%
   dplyr::mutate(
      z_ReappTry = z(ReappTry)
   )
```


```{r}
p00856_mod_z_14 <- lm(z_ReappTry ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3a)

```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_14, key_effects)
```





```{r}
p00856_mod_z_15 <- lm(ZReapSuc ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3a) 

p00856_mod_z_15 %>% summary()
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_15, key_effects)
```





```{r}
p00856_mod_z_16 <- lm(ZNegNoA ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3a)

p00856_mod_z_16 %>% summary()
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_16, key_effects)
```



```{r}
p00856_mod_z_17 <- lm(ZAngry ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3a)
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_17, key_effects)
```



```{r}
p00856_mod_z_18 <- lm(ZAllAct ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3a) 
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_18, key_effects)
```




# Study 3b 

```{r}
p00856_tib_3b %<>%
   dplyr::mutate(
      z_ReappTry = z(ReappTry)
   )
```


```{r}
lm(z(ReappTry) ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + Age + Income, 
   data = p00856_tib_3b) %>% summary()

```

```{r}
lm(ZReapSuc ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + Age + Income, 
   data = p00856_tib_3b) %>% summary()
```

```{r}
lm(ZNegNoA ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + Age + Income, 
   data = p00856_tib_3b) %>% summary()
```

```{r}
lm(ZAngry ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + Age + Income, 
   data = p00856_tib_3b) %>% summary()
```

```{r}
lm(ZAllAct ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + Age + Income, 
   data = p00856_tib_3b) %>% summary()
```


models: 


```{r}
p00856_mod_z_19 <- lm(z_ReappTry ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3b)
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_19, key_effects)
```



```{r}
p00856_mod_z_20 <- lm(ZReapSuc ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3b) 


```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_20, key_effects)
```





```{r}
p00856_mod_z_21 <- lm(ZNegNoA ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3b)
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_21, key_effects)
```



```{r}
p00856_mod_z_22 <- lm(ZAngry ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3b)
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_22, key_effects)
```





```{r}
p00856_mod_z_23 <- lm(ZAllAct ~ as.factor(Cond) + 
     as.factor(Gender) + as.factor(Race_R) + z(Age) + z(Income), 
   data = p00856_tib_3b) 
```

```{r}
key_effects = c("as.factor(Cond)2")
export_ols(p00856_mod_z_23, key_effects)
```


