---
title: ""
output: html_document
---

The capacity to find humorous perspectives in aversive situations may outline a helpful
strategy in the context of cognitive reappraisal. Yet, research suggested that some people
produce more adaptive humour than others. At the same time, not all forms of cognitive reinterpretation
seem to be unequivocally beneficial. The present study aimed to investigate
specific cognitive reappraisal strategies that individuals employ in humorous reappraisal of
adverse events. In a sample of 95 participants, the use of cognitive reappraisal sub-strategies
was assessed in a behavioural test in which participants were required to generate a
series of humorous reappraisals of self-relevant, threatening events. These reappraisal
sub-strategies (three positive reinterpretation strategies, three de-emphasising strategies)
were then related to the habitual use of different kinds of humour as well as the broader
DSM-5 personality trait domains and well-being in terms of depressive experiences,
assessed by self-report questionnaires. While no robust relationships were found for reappraisal
strategies based on de-emphasising, sub-strategies within the positive reinterpretation
category showed specific and contrasting associations with the examined traits.
Findings indicated that the ability to produce humour is only linked to a favourable pattern of
reappraisal strategies when manifested in benign forms of humour. Specific relations also
emerged for the broader personality traits. The study suggests that some characteristics
that advance the use of benign humour also benefit adaptive emotion regulation. The opposite
seems to be true for malicious, or "dark" humour. The introduced behavioural approach
to the analysis of humorous cognitive reappraisal may prove useful also in future related
research.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("../scripts/helpers.R")

library(gtools)
library(robustbase)
library(magrittr) # unless you routinely load tidyverse, in which case leave this one out. You just need it for the pipe. 
library(moments)


variables <- c("paper", "outcome", "n", "skew", "kurt", "z_1.96", "z_2.58", "z_3.29", "mode_n", "var", "var_ratio")

list.files("../data/raw_data/", pattern = "p01193")

p01193_tib <- readxl::read_excel("../data/raw_data/p01193_perchtold2019_pone.0211618.s002.xlsx")

p01193_tib
```

# Malicious humour

```{r}
p01193_mod_original_1 <- lm(dh ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib) 
p01193_mod_original_1 %>% summary()
```

```{r}
p01193_mod_z_1 <- lm(z(dh) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_1 %>% summary()
```

```{r}
key_effects = c("z(pos3)" , "z(pos7)" , "z(pos8)" , "z(rel10)" , "z(rel11)" , "z(rel14)")
export_ols(p01193_mod_z_1, key_effects)
```




# Benign humour


```{r}
p01193_mod_original_2 <- lm(bh ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib) 

p01193_mod_original_2 %>% summary()
```


```{r}
p01193_mod_z_2 <- lm(z(bh) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_2 %>% summary()
```

```{r}
export_ols(p01193_mod_z_2, key_effects)
```



# Depression

```{r}
p01193_mod_original_3 <- lm(ads ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib) 
p01193_mod_original_3 %>% summary()
```

```{r}
p01193_mod_z_3 <- lm(z(ads) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_3 %>% summary()
```

```{r}
export_ols(p01193_mod_z_3, key_effects)
```







# Negative affectivity

```{r}
p01193_mod_original_4 <- lm(naff ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib)
p01193_mod_original_4 %>% summary()
```

```{r}
p01193_mod_z_4 <- lm(z(naff) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_4 %>% summary()
```

```{r}
export_ols(p01193_mod_z_4, key_effects)
```



# Detachment

```{r}
p01193_mod_original_5 <- lm(deta ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib) 
p01193_mod_original_5 %>% summary()
```

```{r}
p01193_mod_z_5 <- lm(z(deta) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_5 %>% summary()
```

```{r}
export_ols(p01193_mod_z_5, key_effects)
```



# Antagonism

```{r}
p01193_mod_original_6 <- lm(anta ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib) 
p01193_mod_original_6 %>% summary()
```


```{r}
p01193_mod_z_6 <- lm(z(anta) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_6 %>% summary()
```

```{r}
export_ols(p01193_mod_z_6, key_effects)
```








# Disinhibition

```{r}
p01193_mod_original_7 <- lm(dis ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib) 
p01193_mod_original_7 %>% summary()
```

```{r}
p01193_mod_z_7 <- lm(z(dis) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_7 %>% summary()
```

```{r}
export_ols(p01193_mod_z_7, key_effects)
```






# Psychoticism

```{r}
p01193_mod_original_8 <- lm(psyc ~ pos3 + pos7 + pos8 + rel10 + rel11 + rel14, 
   data = p01193_tib) 
p01193_mod_original_8 %>% summary()
```

```{r}
p01193_mod_z_8 <- lm(z(psyc) ~ z(pos3) + z(pos7) + z(pos8) + z(rel10) + z(rel11) + z(rel14), 
   data = p01193_tib) 

p01193_mod_z_8 %>% summary()
```

```{r}
export_ols(p01193_mod_z_8, key_effects)
```


