---
title: ""
output: html_document
---

Broad individual differences exist in the ability to create a cognitive map of a new environment. The
current studies investigated whether familiarizing participants with to-be-learned target landmarks
(Experiment 1) or target landmarks plus the order they would be encountered along routes (Experiment
2) before exploring the Silcton virtual environment would increase performance on tasks assaying spatial
memory of Silcton. Participants in both experiments were randomly assigned to be pre-exposed either to
information about target landmarks in Silcton or control landmarks on the university campus. In both
experiments, participants explored Silcton via four prescribed routes and then performed a direction
estimation task and a map building task based on memory for the locations of the target landmarks. In
addition, participants completed the Spatial Orientation Test of perspective-taking. Pre-exposure to
Silcton landmarks versus control landmarks did not affect scores on Silcton-based tasks in either
experiment. Some sex differences in direction estimation were observed in Experiment 1 but not
Experiment 2. While facilitating familiarity with landmarks did not improve cognitive map accuracy,
both sex and perspective taking ability were found to contribute to individual differences in the ability
to create a cognitive map.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magrittr)
source("../scripts/helpers.R")

library(gtools)
library(robustbase)
library(magrittr) # unless you routinely load tidyverse, in which case leave this one out. You just need it for the pipe. 
library(moments)


variables <- c("paper", "outcome", "n", "skew", "kurt", "z_1.96", "z_2.58", "z_3.29", "mode_n", "var", "var_ratio")


list.files("../data/raw_data/", pattern = "p01136")

p01136_tib <- readxl::read_excel(
  "../data/raw_data/p01136_youngson2019_Master Data Sheet for Landmark Familiarity Study 1.xlsx"
) %>% 
  dplyr::filter(!is.na(Sex))

p01136_tib
```

# Experiment 1 

follow-up ANOVAs

There's an undisclosed removal of a participant (dfs don't match). I've ran "leave-one-out" by none of the values match the reported ones exactly. 

```{r}
p01136_mod_original_1 <- lm(ModelBuild ~ as.factor(Sex) + as.factor(Group), data = p01136_tib)
p01136_mod_original_1 %>% car::Anova(type = 3)
p01136_mod_original_1 %>% summary()
```

```{r eval = FALSE}
for(i in unique(p01136_tib$Subject)){
  
  print(
    list(
      i,
      lm(ModelBuild ~ as.factor(Sex) + as.factor(Group), 
         data = filter(p01136_tib, Subject != i)) %>% 
        car::Anova(type = 3)
    )
  )
  
}
```

```{r}
p01136_mod_z_1 <- lm(z(ModelBuild) ~ as.factor(Sex) + as.factor(Group), data = p01136_tib)
p01136_mod_z_1 %>% car::Anova(type = 3)
p01136_mod_z_1 %>% summary()
```
```{r}
key_effects = c("as.factor(Group)2")
export_ols(p01136_mod_z_1, key_effects)
```









```{r}
p01136_mod_original_2 <- lm(OffsiteDiff ~ as.factor(Sex) + as.factor(Group), data = p01136_tib)
p01136_mod_original_2 %>% car::Anova(type = 3)
p01136_mod_original_2 %>% summary()
```

```{r}
p01136_mod_z_2 <- lm(z(OffsiteDiff) ~ as.factor(Sex) + as.factor(Group), data = p01136_tib)
p01136_mod_z_2 %>% car::Anova(type = 3)
p01136_mod_z_2 %>% summary()
```

```{r}
key_effects = c("as.factor(Group)2")
export_ols(p01136_mod_z_2, key_effects)
```








```{r}
p01136_mod_original_3 <- lm(KendallsTau ~ as.factor(Sex) + as.factor(Group), data = p01136_tib)
p01136_mod_original_3 %>% summary()
```

```{r}
p01136_mod_z_3 <- lm(z(KendallsTau) ~ as.factor(Sex) + as.factor(Group), data = p01136_tib)
p01136_mod_z_3 %>% summary()
```

```{r}
key_effects = c("as.factor(Group)2")
export_ols(p01136_mod_z_3, key_effects)
```







```{r}
p01136_mod_original_4 <- lm(OffsiteSame ~ as.factor(Sex) + as.factor(Group), data = p01136_tib) 
p01136_mod_original_4 %>% summary()
```

```{r}
p01136_mod_z_4 <- lm(z(OffsiteSame) ~ as.factor(Sex) + as.factor(Group), data = p01136_tib)
p01136_mod_z_4 %>% summary()
```

```{r}
key_effects = c("as.factor(Group)2")
export_ols(p01136_mod_z_4, key_effects)
```


regression

```{r}
p01136_mod_original_5 <- lm(ModelBuild ~ as.factor(Sex) + SOT, data = p01136_tib)
p01136_mod_original_5 %>% summary()
```

```{r}
p01136_mod_z_5 <- lm(z(ModelBuild) ~ as.factor(Sex) + z(SOT), data = p01136_tib)
p01136_mod_z_5 %>% summary()
```

```{r}
key_effects = c("as.factor(Sex)2", "z(SOT)")
export_ols(p01136_mod_z_5, key_effects)
```