---
title: ""
output: html_document
---

Gateway Groups are characterized by a unique social categorization which enables them to be identified with two or more groups
within the context of intergroup relations. Due to their strategic situation, Gateway Groups have been found to have the potential to improve
the relations between their distinct social counterparts. In this paper we attempted to replicate the Gateway Group line of research in the
Western Balkan context with two different kinds of Gateway Groups: Children of mixed Serb(s) and Bosniak families, and Bosniak citizens of
Serbia. As in previous Gateway Group studies, we found that in both cases the exposure to a dually identified Gateway Group lead to a more
complex perception of the Gateway Group itself, a higher belief in the potential of the Gateway Group to bridge the relations between the
ingroup and the outgroup, and a greater sense of closeness between the ingroup and the outgroup.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("../scripts/helpers.R")

library(gtools)
library(robustbase)
library(magrittr) # unless you routinely load tidyverse, in which case leave this one out. You just need it for the pipe. 
library(moments)


variables <- c("paper", "outcome", "n", "skew", "kurt", "z_1.96", "z_2.58", "z_3.29", "mode_n", "var", "var_ratio")

list.files("../data/raw_data/", pattern = "p01235")

p01235_tib_1 <- haven::read_sav("../data/raw_data/p01235_levy2019_Study 1 GG Balkans - Raw data and Scales.sav") 
p01235_tib_2 <- haven::read_sav("../data/raw_data/p01235_levy2019_Study 2 GG Balkans - Raw data and Scales.sav") 

names(p01235_tib_1)
```

```{r}
p01235_tib_1 %<>% 
  dplyr::mutate(
    SIC = rowMeans(.[c("SIC1", "SIC2", "SIC3", "SIC4", "SIC5", "SIC6")])
  )

p01235_tib_2 %<>% 
  dplyr::mutate(
    SIC = rowMeans(.[c("SIC1", "SIC2", "SIC3", "SIC4", "SIC5", "SIC6")])
  )
```


# Study 1 

```{r}
p01235_mod_original_1 <- lm(DUAL_ID_SCL ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_original_1 %>% summary()
```

```{r}
p01235_mod_z_1 <- lm(z(DUAL_ID_SCL) ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_z_1 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)1")
export_ols(p01235_mod_z_1, key_effects)
```






```{r}
p01235_mod_original_2 <- lm(BRIDGE ~ as.factor(Condition), data = p01235_tib_1)
p01235_mod_original_2 %>% summary()
```

```{r}
p01235_mod_z_2 <- lm(z(BRIDGE) ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_z_2 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)1")
export_ols(p01235_mod_z_2, key_effects)
```







```{r}
p01235_mod_original_3 <- lm(SIC ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_original_3 %>% summary()
```

```{r}
p01235_mod_z_3 <- lm(z(SIC) ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_z_3 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)1")
export_ols(p01235_mod_z_3, key_effects)
```




```{r}
p01235_mod_original_4 <- lm(CLOSENESS ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_original_4 %>% summary()
```

```{r}
p01235_mod_z_4 <- lm(z(CLOSENESS) ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_z_4 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)1")
export_ols(p01235_mod_z_4, key_effects)
```






```{r}
p01235_mod_original_5 <- lm(SD_SCL ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_original_5 %>% summary()
```

```{r}
p01235_mod_z_5 <- lm(z(SD_SCL) ~ as.factor(Condition), data = p01235_tib_1) 
p01235_mod_z_5 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)1")
export_ols(p01235_mod_z_5, key_effects)
```


# Study 2

```{r}
names(p01235_tib_2)
```


```{r}
p01235_mod_original_6 <- lm(DUAL_ID_SCL ~ as.factor(Condition), data = p01235_tib_2)
p01235_mod_original_6 %>% summary()
```

```{r}
p01235_mod_z_6 <- lm(z(DUAL_ID_SCL) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_6 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_6, key_effects)
```





```{r}
p01235_mod_original_7 <- lm(GG_Level ~ as.factor(Condition), data = p01235_tib_2)
p01235_mod_original_7 %>% summary()
```

```{r}
p01235_mod_z_7 <- lm(z(GG_Level) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_7 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_7, key_effects)
```



```{r}
p01235_mod_original_8 <- lm(BRIDGEGG_SCL ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_original_8 %>% summary()
```

```{r}
p01235_mod_z_8 <- lm(z(BRIDGEGG_SCL) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_8 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_8, key_effects)
```






```{r}
p01235_mod_original_9 <- lm(BRIDGEGG1 ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_original_9 %>% summary()
```

```{r}
p01235_mod_z_9 <- lm(z(BRIDGEGG1) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_9 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_9, key_effects)
```





```{r}
p01235_mod_original_10 <- lm(BRIDGEGG2 ~ as.factor(Condition), data = p01235_tib_2)
p01235_mod_original_10 %>% summary()
```

```{r}
p01235_mod_z_10 <- lm(z(BRIDGEGG2) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_10 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_10, key_effects)
```






```{r}
p01235_mod_original_11 <- lm(SIC ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_original_11 %>% summary()
```

```{r}
p01235_mod_z_11 <- lm(z(SIC) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_11 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_11, key_effects)
```




```{r}
p01235_mod_original_12 <- lm(CLOSENESS ~ as.factor(Condition), data = p01235_tib_2)
p01235_mod_original_12 %>% summary()
```

```{r}
p01235_mod_z_12 <- lm(z(CLOSENESS) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_12 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_12, key_effects)
```





```{r}
p01235_mod_original_13 <- lm(SD_SCL ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_original_13 %>% summary()
```

```{r}
p01235_mod_z_13 <- lm(z(SD_SCL) ~ as.factor(Condition), data = p01235_tib_2) 
p01235_mod_z_13 %>% summary()
```

```{r}
key_effects = c("as.factor(Condition)2")
export_ols(p01235_mod_z_13, key_effects)
```
