---
title: ""
output: html_document
---

A variety of studies have demonstrated gains in cognitive ability following cognitive training
interventions. However, other studies have not shown such gains, and questions remain
regarding the efficacy of specific cognitive training interventions. Cognitive training research
often involves programs made up of just one or a few exercises, targeting limited and specific
cognitive endpoints. In addition, cognitive training studies typically involve small samples
that may be insufficient for reliable measurement of change. Other studies have
utilized training periods that were too short to generate reliable gains in cognitive
performance.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("../scripts/helpers.R")

library(gtools)
library(robustbase)
library(magrittr) # unless you routinely load tidyverse, in which case leave this one out. You just need it for the pipe. 
library(moments)


variables <- c("paper", "outcome", "n", "skew", "kurt", "z_1.96", "z_2.58", "z_3.29", "mode_n", "var", "var_ratio")

list.files("../data/raw_data/", pattern = "p03274")

p03274_tib <- readr::read_csv("../data/raw_data/p03274_hardy2016_pone.0134467.s004.csv") %>%
  dplyr::filter(exclude == 0)

p03274_tib
```


```{r}
p03274_mod_original_1 <- lm(GI_d ~ group + GI_1, data = p03274_tib) 
p03274_mod_original_1 %>% summary()
```

```{r}
p03274_mod_z_1 <- lm(z(GI_d) ~ group + z(GI_1), data = p03274_tib) 
p03274_mod_z_1 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_1, key_effects)
```






```{r}
p03274_mod_original_2 <- lm(MS_d ~ group + MS_1, data = p03274_tib)
p03274_mod_original_2 %>% summary()
```

```{r}
p03274_mod_z_2 <- lm(z(MS_d) ~ group + z(MS_1), data = p03274_tib) 
p03274_mod_z_2 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_2, key_effects)
```







```{r}
p03274_mod_original_3 <- lm(RMS_d ~ group + RMS_1, data = p03274_tib) 
p03274_mod_original_3 %>% summary()
```

```{r}
p03274_mod_z_3 <- lm(z(RMS_d) ~ group + z(RMS_1), data = p03274_tib) 
p03274_mod_z_3 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_3, key_effects)
```





```{r}
p03274_mod_original_4 <- lm(GR_d ~ group + GR_1, data = p03274_tib)
p03274_mod_original_4 %>% summary()
```

```{r}
p03274_mod_z_4 <- lm(z(GR_d) ~ group + z(GR_1), data = p03274_tib) 
p03274_mod_z_4 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_4, key_effects)
```






```{r}
p03274_mod_original_5 <- lm(PM_d ~ group + PM_1, data = p03274_tib)
p03274_mod_original_5 %>% summary()
```

```{r}
p03274_mod_z_5 <- lm(z(PM_d) ~ group + z(PM_1), data = p03274_tib) 
p03274_mod_z_5 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_5, key_effects)
```




```{r}
p03274_mod_original_6 <- lm(GNG_d ~ group + GNG_1, data = p03274_tib)
p03274_mod_original_6 %>% summary()
```

```{r}
p03274_mod_z_6 <- lm(z(GNG_d) ~ group + z(GNG_1), data = p03274_tib) 
p03274_mod_z_6 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_6, key_effects)
```




```{r}
p03274_mod_original_7 <- lm(AR_d ~ group + AR_1, data = p03274_tib)
p03274_mod_original_7 %>% summary()
```

```{r}
p03274_mod_z_7 <- lm(z(AR_d) ~ group + z(AR_1), data = p03274_tib) 
p03274_mod_z_7 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_7, key_effects)
```






```{r}
p03274_mod_original_8 <- lm(TTS_d ~ group + TTS_1, data = p03274_tib)
p03274_mod_original_8 %>% summary()
```

```{r}
p03274_mod_z_8 <- lm(z(TTS_d) ~ group + z(TTS_1), data = p03274_tib) 
p03274_mod_z_8 %>% summary()
```

```{r}
key_effects = c("grouplumosity")
export_ols(p03274_mod_z_8, key_effects)
```
