---
title: "u02896_pollet2020"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

Verbal denigration of personal body size and shape ("fat talk") is
correlated with, and can 16 have a causal influence on body
dissatisfaction and disordered eating. What is less clear is 17 who is
most likely to fat talk. To address this, Corning and Gondoli (2012)
conducted a 18 study confirming that a woman's body dissatisfaction
directly predicted their fat talk. But 19 this effect was scaled so that
the likelihood of engaging in fat talk intensified if she had a 20
stronger tendency to socially compare: the relationship was
multiplicative. Here, we carried 21 out two replications of Corning and
Gondoli's (2012) study, the first with 189 UK 22 participants and the
second with 371 US participants. We found that multiple regression 23
models predicting fat talk showed additive, but not multiplicative
relationships. A mini 24 meta-analysis combining the results of our two
studies with the results of the original study 25 confirmed this. A
power simulation suggested that the original claim of a significant 26
interaction term was probably a false positive. In conclusion, these
studies show an additive 27 relationship between fat talk and social
comparison on fat talk. We discuss how 28 multiplicative relationships
may occur and why they matter clinically if they do exist.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(haven) # comment
require(readxl)
require(dplyr)
require(magrittr)
require(skimr)
require(psych)
require(stargazer)
require(tidyimpute)
require(tidyr)
require(sjlabelled)
require(apaTables)
require(sjPlot)
require(sjmisc)
require(jtools)
require(sandwich) # Robust estimation.
require(lmtest)
require(ggplot2)
require(ggthemes)
require(readxl)
require(esc)
require(metafor)
require(meta)
require(interactions)
require(rockchalk)
require(cowplot)
require(car)
require(performance)

```

# Study 1: Data Wrangling

```{r}
Study1 <- read_xlsx("../data/raw_data/r02896_pollet2020_1.xlsx") 
```

197 reached the end of the survey

```{r}
Study1 %<>% filter(is.na(Q43)==F)
```

8 participants did not provide height or weight.

```{r}
Study1 %<>% filter(is.na(Weight_kg)==F)
Study1 %<>% filter(is.na(Height_cm)==F)
```

```{r}
mean(Study1$Q4)
sd(Study1$Q4)
min(Study1$Q4)
max(Study1$Q4)
```

# Study 1: BMI

```{r}
Study1 %<>% mutate(BMI = ((Weight_kg/Height_cm/Height_cm) * 10000))
```

# Study 1: Sum scales.

Note that this overrides (!!!).

## EDI recode

```{r}
Study1$Q6 <- car::recode(Study1$Q6, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q15 <- car::recode(Study1$Q15, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q16 <- car::recode(Study1$Q16, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q19 <- car::recode(Study1$Q19, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q21 <- car::recode(Study1$Q21, "1=5; 2=4; 3=3; 4=2; 5=1")
```

## INCOM

Qualtrics had scored 1 = always, never = 5 so we recode here. Therefore
we rescore all but Q27/Q33.

```{r}
Study1$Q23 <- car::recode(Study1$Q23, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q24 <- car::recode(Study1$Q24, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q25 <- car::recode(Study1$Q25, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q26 <- car::recode(Study1$Q26, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q28 <- car::recode(Study1$Q28, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q29 <- car::recode(Study1$Q29, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q30 <- car::recode(Study1$Q30, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q31 <- car::recode(Study1$Q31, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q32 <- car::recode(Study1$Q32, "1=5; 2=4; 3=3; 4=2; 5=1")
```

## Fat Talk.

Qualtrics had scored 1 = always, never = 5 so we recode here.

```{r}
Study1$Q35 <- car::recode(Study1$Q35, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q36 <- car::recode(Study1$Q36, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q37 <- car::recode(Study1$Q37, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q38 <- car::recode(Study1$Q38, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q39 <- car::recode(Study1$Q39, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q40 <- car::recode(Study1$Q40, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q41 <- car::recode(Study1$Q41, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q42 <- car::recode(Study1$Q42, "1=5; 2=4; 3=3; 4=2; 5=1")
Study1$Q43 <- car::recode(Study1$Q43, "1=5; 2=4; 3=3; 4=2; 5=1")
```

```{r}
Study1 %<>% mutate(EDI= rowSums(subset(select(Study1, c(Q6:Q21)))))
Study1 %<>% mutate(INCOM= rowSums(subset(select(Study1, c(Q23:Q33)))))
Study1 %<>% mutate(Fat_talk= rowSums(subset(select(Study1, c(Q35:Q43)))))
```

# Study 1: Centered variables.

Centered the variables.

```{r}
Study1 %<>% mutate(EDI_cent= EDI-mean(EDI), INCOM_cent= INCOM-mean(INCOM), BMI_cent= BMI-mean(BMI), Fat_talk_cent= Fat_talk-mean(Fat_talk)) # center
Study1 %<>% mutate(EDI_cent_z= scale(EDI_cent), INCOM_cent_z= scale(INCOM_cent), BMI_cent_z= scale(BMI_cent), Fat_talk_cent_z= scale(Fat_talk_cent)) # z_score
```

# Study 1: Multiple regression, Fat talk

Standardised coefficients

```{r}
Study1 <- Study1 |> 
  dplyr::mutate(
    dplyr::across(
      .cols = c(Fat_talk_cent_z, BMI_cent_z, EDI_cent_z, INCOM_cent_z), 
      .fns = as.numeric
    )
  )

Study1$BMI_cent_z |> class()
```


```{r}
#model_2_f <-lm(Fat_talk_cent_z ~ BMI_cent_z + EDI_cent_z + INCOM_cent_z-1, data=Study1)
model_3_f <-lm(Fat_talk_cent_z ~ BMI_cent_z + EDI_cent_z * INCOM_cent_z-1, data=Study1)
```

# ------ HERE

```{r}
summary(model_3_f)
```

```{r}
r02896_mod_z_1 <- model_3_f
key_effects = c("BMI_cent_z", "EDI_cent_z", "INCOM_cent_z", "EDI_cent_z:INCOM_cent_z")
export_ols(r02896_mod_z_1, key_effects)
```


note down variables:

```{r}
Study1$Fat_talk_cent_z
Study1$BMI_cent_z
Study1$EDI_cent_z
Study1$INCOM_cent_z
```

# Study 2

```{r}
Study2<-read_xlsx("../data/raw_data/r02896_pollet2020_2.xlsx") 
```

376 reached the end of the survey

```{r}
Study2 %<>% filter(is.na(Q43)==F)
```

```{r}
Study2 %<>% filter(is.na(Weight_kg)==F)
Study2 %<>% filter(is.na(Height_cm)==F)
```

```{r}
Study2 %<>% filter(Woman==4)
```

# Study 2 : BMI

```{r}
Study2 %<>% mutate(BMI = ((Weight_kg/Height_cm/Height_cm) * 10000))
```

There are some extreme values here. Therefore we also Winsorised the BMI
data.

```{r}
sum(Study2$BMI > 18.5 & Study2$BMI < 24.9) / nrow(Study2) # normal weight
sum(Study2$BMI < 18.5) / nrow(Study2) # underweight
sum(Study2$BMI > 25 & Study2$BMI < 29.9) / nrow(Study2) # overweight
sum(Study2$BMI > 30) / nrow(Study2) # obese
```

# Study 2: Sum scales.

Note that this overrides (!!!).

## EDI recode

```{r}
Study2$Q6 <- car::recode(Study2$Q6, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q15 <- car::recode(Study2$Q15, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q16 <- car::recode(Study2$Q16, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q19 <- car::recode(Study2$Q19, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q21 <- car::recode(Study2$Q21, "1=5; 2=4; 3=3; 4=2; 5=1")
```

## INCOM

Qualtrics had scored 1 = always, never = 5 so we recode here. Therefore
we rescore all but Q27/Q33.

```{r}
Study2$Q23 <- car::recode(Study2$Q23, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q24 <- car::recode(Study2$Q24, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q25 <- car::recode(Study2$Q25, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q26 <- car::recode(Study2$Q26, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q28 <- car::recode(Study2$Q28, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q29 <- car::recode(Study2$Q29, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q30 <- car::recode(Study2$Q30, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q31 <- car::recode(Study2$Q31, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q32 <- car::recode(Study2$Q32, "1=5; 2=4; 3=3; 4=2; 5=1")
```

## Fat Talk.

Qualtrics had scored 1 = always, never = 5 so we recode here.

```{r}
Study2$Q35 <- car::recode(Study2$Q35, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q36 <- car::recode(Study2$Q36, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q37 <- car::recode(Study2$Q37, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q38 <- car::recode(Study2$Q38, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q39 <- car::recode(Study2$Q39, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q40 <- car::recode(Study2$Q40, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q41 <- car::recode(Study2$Q41, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q42 <- car::recode(Study2$Q42, "1=5; 2=4; 3=3; 4=2; 5=1")
Study2$Q43 <- car::recode(Study2$Q43, "1=5; 2=4; 3=3; 4=2; 5=1")
```

```{r}
Study2 %<>% mutate(EDI= rowSums(subset(select(Study2, c(Q6:Q21)))))
Study2 %<>% mutate(INCOM= rowSums(subset(select(Study2, c(Q23:Q33)))))
Study2 %<>% mutate(Fat_talk= rowSums(subset(select(Study2, c(Q35:Q43)))))
```

# Study 2: Centered variables.

Centered the variables.

```{r}
Study2 %<>% mutate(EDI_cent= EDI-mean(EDI), INCOM_cent= INCOM-mean(INCOM), BMI_cent= BMI-mean(BMI), Fat_talk_cent= Fat_talk-mean(Fat_talk)) # center
Study2 %<>% mutate(EDI_cent_z= scale(EDI_cent), INCOM_cent_z= scale(INCOM_cent), BMI_cent_z= scale(BMI_cent), Fat_talk_cent_z= scale(Fat_talk_cent)) # z_score
```

# Study 2: Multiple regression, Fat talk

Standardised coefficients


```{r}
Study2 <- Study2 |> 
  dplyr::mutate(
    dplyr::across(
      .cols = c(Fat_talk_cent_z, BMI_cent_z, EDI_cent_z, INCOM_cent_z), 
      .fns = as.numeric
    )
  )

Study2$BMI_cent_z |> class()
```


```{r}
model_1_f<-lm(Fat_talk_cent_z~BMI_cent_z-1,data=Study2)
model_2_f<-lm(Fat_talk_cent_z~BMI_cent_z+EDI_cent_z+INCOM_cent_z-1,data=Study2)
model_3_f<-lm(Fat_talk_cent_z~BMI_cent_z+EDI_cent_z*INCOM_cent_z-1,data=Study2)
```

# ----- HERE

```{r}
summary(model_3_f)
```

```{r}
r02896_mod_z_2 <- model_3_f
key_effects = c("BMI_cent_z", "EDI_cent_z", "INCOM_cent_z", "EDI_cent_z:INCOM_cent_z")
export_ols(r02896_mod_z_2, key_effects)
```