---
title: "Untitled"
author: "MS"
date: '2022-08-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("../scripts/helpers.R")

df_1 <- readRDS("../data/raw_data/u00613_clean_mcs_personality.rds")
df_2 <- readRDS("../data/raw_data/u00613_morbid_genres_z.rds")
```

(study 1 is FA)

# study 2

model 1 

- estimates in the model seem unstandardised whereas these were standardised (even before I applied the z function)

```{r}
u00613_mod_z_1 <- lm(z(morbid_curiosity) ~ 
                       z(FDC_overt_social)  + 
                       z(honhum_score) +
                       z(animal_reminder_disgust) +
                       z(PPI_FEAR) + z(PPI_REBEL) + z(PPI_STRESS) +
                       factor(sex) + z(age), 
                     data = df_1)



export_ols(u00613_mod_z_1, 
           key_effects = mod_coeffs(u00613_mod_z_1)[1:6])
```

# Study 3 

these are already in z scores 

 MCS and TIPI
 
 model 2
 
```{r}
u00613_mod_z_2 <- lm(morbid_curiosity ~ emotionality + conscientiousness + agreeableness + extraversion + openness,
                     data = df_2)

export_ols(u00613_mod_z_2, key_effects = mod_coeffs(u00613_mod_z_2))
```

genres

model 3

```{r}
u00613_mod_z_3 <- lm(alien ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_3, key_effects = "morbid_curiosity")
```

model 4

```{r}
u00613_mod_z_4 <- lm(apocalyptic ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_4, key_effects = "morbid_curiosity")
```

model 5

```{r}
u00613_mod_z_5 <- lm(comedy ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_5, key_effects = "morbid_curiosity")
```

model 6

```{r}
u00613_mod_z_6 <- lm(crime ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_6, key_effects = "morbid_curiosity")
```

model 7

```{r}
u00613_mod_z_7 <- lm(horror ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_7, key_effects = "morbid_curiosity")
```

model 8

```{r}
u00613_mod_z_8 <- lm(romance ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_8, key_effects = "morbid_curiosity")
```

model 9

```{r}
u00613_mod_z_9 <- lm(scifi ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_9, key_effects = "morbid_curiosity")
```

model 10

```{r}
u00613_mod_z_10 <- lm(supernatural ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_10, key_effects = "morbid_curiosity")
```

model 11

```{r}
u00613_mod_z_11 <- lm(thriller ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_11, key_effects = "morbid_curiosity")
```

model 12

```{r}
u00613_mod_z_12 <- lm(zombie ~ morbid_curiosity + 
                       factor(sex) + age + income + 
                       emotionality + conscientiousness + agreeableness + extraversion + openness,
          data = df_2)

export_ols(u00613_mod_z_12, key_effects = "morbid_curiosity")
```

# study 4

I can't get study 4 to reproduce - something's not right in the processing script and the results don't match (the pattern on the ggplot is odd.)